\chapter{Introduction}

Steam~\cite{steam} is the world's most popular PC game distribution platform that has 67 million monthly active players. Since January 2016, Steam has experienced a whooping 27 million first time purchasers. According to steamspy, there are currently $26,363$ games available on Steam. Each of these games fall under different categories and contains different features such as backgrounds, emotes and cards. Furthermore, the prices of these games also vary over the course of time. These information become important for a user wanting to purchase a game from Steam. However, such information are not always present in a clear and concise manner on the Steam website. 

The idea behind gTrack is to have a dedicated website built using Ruby on Rails~\cite{ror} meant to serve interested users who would like to access a game on Steam. on gTrack, unauthenticated users get to see a list of all available games on Steam. Such user also get to see the ratings associated with the games. Once authenticated, users get to check necessary information such as price, genre, backgrounds, emotes and cards of the games. Users are also offered a search feature using which games could be sorted based on different categories. Additionally, users are allowed to comment on a game, see comments of other users about a game, up vote or down vote a game and interact with other users using a chat room. The sole purpose of this website is to deliver as much information about a game as possible to a user to facilitate her decision process while accessing/buying a game from Steam.

As Steam has a huge user base, it is practical to assume that a website such as gTrack would also draw attention of many such users. As such, scalability of the website with increasing number of users becomes a key issue. In this report, we first present some of the features available in our website. We then proceed to present the findings of various load tests we conducted to determine possible bottlenecks in our website. We present the results of various load tests and discuss the results in details.  

